A word-sense representation for documents based on information value and word sense disambiguation

### 2014-04-02 paper/refactor.tex
results text added

\input{handpicked_table}
\section{Results}
This section is divided in two: first, we present the \textit{top senses} of the documents listed in ``Text corpus''; second, we present the similarities between the documents and the word-senses evaluation set.

@@

ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT

>>>>

\input{handpicked_table}
\newpage

\section{Results}
This section is divided in two: first, we present the \textit{top senses} of the documents listed in ``Text corpus''; second, we present the similarities between the documents and the word-senses evaluation set.

@@

On $Top-senses$ table we can observe that some senses like local\_anesthetic was matched on Whats to be done? as first result. \\
Also on State and revolution Marx was matched with a United States comedian and a similar result we got with Berstein that was matched with a composer, however in the case of Engels it was matched to a socialist who wrote the Communist Manifesto with Karl Marx. \\
$Similarities$ tables shows that, in most of the works, synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ had a lower similarity on most of the works. \\
One strange result was $Hair$ that matched second in similarity score in Imperialism, the Highest St....
